Run AwAI: StarCraftII Adversary Avoidance Using Neural Networks and Genetic Algorithms

### 2018-06-06 doc/run_awai.tex
fixed image formatting
added abstract

\begin{abstract}
  \textbf{Abstract}: \blindtext
  \\~\\
  \textbf{Keywords}: Machine Learning, Genetic Algorithms, Neural Networks,
  StarCraftII
\end{abstract}
\\~\\
\hline
\\~\\

@@

% The Pysc2 interface allowed us to create an agent to interact with the Star
% Craft II game.  The agent class contains a \texttt{step()} function that is
% called several times per second of game time. This meant that all of the actions
% the agent took had to be in this step function, and thus this is where we would
% integrate our neural net.  We decided to use the mini game map DefeatRoaches,
% which is included with Pysc2 as a base for our simulation environment. By
% heavily relying on a preexisting map and mini game, we could focus more of our
% time and resources on developing the genetic algorithm and neural network
% implementation.

% To make our controller implementation as modular as possible, we decided to
% provide a dictionary of inputs and receive a dictionary of outputs. The inputs
% would be the x and y coordinates of the agent’s units, as well as the x and y
% coordinates of the enemy units. The inputs had to be created and assembled into
% a dictionary in the step function.  In order to normalize the inputs, we divided
% the coordinate value by the maximum map size in the corresponding axis.  To
% obtain the values for the inputs, we created a series of methods for our agent
% class.  These methods include \texttt{getCurrentLocation()} and
% \texttt{getCurrentEnemeyLocation}().  We also created methods to move the
% friendly units, including \texttt{moveToLocation()} and setTargetDestination.
% These functions could be used together to set a target destination coordinate
% and cause the friendly units to move toward that target.

@@

% Whenever \texttt{step()} is called by Pysc2, the first thing we do is check the
% observable action space. If friendly unit movement is not an option, this means
% the unit(s) are not selected.  If units are not selected, this means it is the
% first time the \texttt{step()} function is being called in the simulation
% episode.  In this case, in addition to selecting the units, we also reset
% various counters (such as steps survived).  During the first call of
% \texttt{step()}, we also unpickle a neural network file.

@@

% In the case where \texttt{step()} is called and units are already selected, the
% \texttt{moveToLocation()} function is called.  Initially, we set the target
% destination to the enemy location.  We have our units move directly to the
% hostile units in order to engage them in combat, and this initiate a pursuit
% from the enemy.  We felt this would be the most direct way to initiate a
% pursuit.  We investigated running two Pysc2 agents against each other, however
% Pysc2 currently only support the simulation of one custom agent at a time. Once
% the friendly units arrive at their destination, the \texttt{moveToLocation()}
% function returns an arrived at target status to the calling \texttt{step()}
% function.

@@

%% Fix
To evaluate the fitness of the neural network, we count the number of steps that
the units survived for.  One problem we encountered and solved, was the initial
series of steps taken before engaging the enemy units. For example, the
DefeatRoaches map spawns the enemy and friendly units on opposite sides of the
map, in a random selection of several predefined start locations.  However, the
distance between these start locations can vary between simulation episode.
This means our neural network fitness (number of steps survived) could be
slightly affected by an irrelevant condition.  To mitigate this issue, we
subtract the number of steps it takes until the friendly units reach their first
destination (the location of the enemy units) and start their engagement. By
only counting steps after enemy engagement has begun, our fitness function is
more reflective of survival time.

% In order for our evolutionary genetic algorithm to evolve, the end fitness of a
% network must be returned from the Pysc2 simulation.  Our simulation runs a
% configurable (up to 55) episodes per individual (neural network) and averages
% the fitness for all of those simulation episodes. We played with the number of
% simulation episodes per simulation test, exploring the tradeoff between
% simulation runtime and precision.  In the future, we could explore modifying our
% fitness function to incorporate more meaning from having multiple simulation
% episodes.  One future idea we had was to see if the group of individual survival
% times were skewed above or below the mean.

>>>>

\begin{abstract}
  \textbf{Abstract}:

  This project explores the integration of a neural network and an evolutionary
  genetic algorithm with the Star Craft II API.The goal of this project was to
  successfully control a StarCraft II agent via a neural network, and maximize
  its fitness through a genetic evolutionary algorithm. The agent uses the PySC2
  API to connect with StarCraft II, and a neural network to control its
  actions.The fitness function is defined as the survival duration for an agent
  in a sandbox environment with hostile units, where surviving for longer is
  better.The action space of the agent was limited to movement in order to
  achieve a realistic scope for the project.The fitness of an individual is
  evaluated by running multiple simulation episodes and averaging the
  performance (survival time) for each episode.The neural network uses an
  explicit topologically unrestricted implementation.This implementation
  provides high degrees of freedom while minimizing the network size.The genetic
  algorithm uses tournament selection to select the most fit neural network
  (individuals) to breed.Each successive generation of neural networks is
  slightly better at surviving in the hostile sandbox environment.After 50
  iterative generations, our resulting neural network had increased the average
  survival time of an agent by 288%.

  \\~\\
  \textbf{Keywords}: Machine Learning, Genetic Algorithms, Neural Networks,
  StarCraftII
\end{abstract}
\\~\\
\hline
\\~\\

@@

@@

@@

@@

To evaluate the fitness of the neural network, we count the number of steps that
the units survived for.  One problem we encountered and solved, was the initial
series of steps taken before engaging the enemy units. For example, the
DefeatRoaches map spawns the enemy and friendly units on opposite sides of the
map, in a random selection of several predefined start locations.  However, the
distance between these start locations can vary between simulation episode.
This means our neural network fitness (number of steps survived) could be
slightly affected by an irrelevant condition.  To mitigate this issue, we
subtract the number of steps it takes until the friendly units reach their first
destination (the location of the enemy units) and start their engagement. By
only counting steps after enemy engagement has begun, our fitness function is
more reflective of survival time.
